---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
params:
  github: "https://github.com/cfbuenabadn/leafcutter2_paper/blob/main/"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message=F)
```

Code and figures for the LeafCutter2 paper: annotation-free classification of splice
junctions as productive or unproductive, and what that classification reveals about
tissue-specific gene regulation, cross-species conservation, and disease risk.

See the [repository README](https://github.com/cfbuenabadn/leafcutter2_paper) for what
each figure is built from. Figure 3 and the Supplementary Note 1 benchmark live in
separate bundles:
[comparative splicing](https://bfairkun.github.io/20260825_comparativesplicing_paper/ComparativeSplicingFigures.html),
[simulation benchmark](https://bfairkun.github.io/20260825_leaf2simulation_paper/SimulationBenchmarkFigures.html).

## Rendered figure notebooks

Every panel, with the code that made it:

```{r, results = 'asis', echo = FALSE}
library(tidyverse)
htmls <- list.files(path = "../docs/", pattern="^.+\\.html$") %>%
  str_replace("^(.+?)\\.html$", "\\1") %>%
  str_subset(pattern = "^about$|^index$|^license$", negate = TRUE)
for(fn in htmls){
  cat("[", fn, "](", fn,".html)\n\n", sep="")
}
```

## Source notebooks on GitHub

```{r,  results = 'asis', echo = FALSE}
# Only notebooks that are actually tracked -- analysis/ keeps plenty of
# untracked scratch copies, and linking those would give 404s on GitHub.
ipynbs <- tryCatch(
  system("git ls-files '*.ipynb'", intern = TRUE),
  warning = function(w) character(0), error = function(e) character(0))
ipynbs <- sort(ipynbs[!grepl("checkpoint", ipynbs)])

for(fn in ipynbs){
  cat("[", fn, "](", params$github, "analysis/", fn, ")\n\n", sep="")
}

```


